Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-27 doc/JFLA2022/paper.tex
more explanations (minoration of the length of a battle)

Using $H'$s equations as rewrite rules, we can study a concrete example of hydra battle. Let us start with the hydra of figure~\ref{fig:start} and $0$ as initial step.
By a combination of rewriting and induction, we prove that the number of steps of the considered battle has at least $2^{10^{21}}$ binary digits.

>>>>

Using $H'$s equations as rewrite rules, we can study a concrete example of hydra battle. Let us start with the hydra of figure~\ref{fig:start} and $0$ as initial step.
By a sequence of rewritings and induction proof steps, we prove that the number of steps of the considered battle is greater or equal than $2^{2^N}$, where $N=2^{70}-1$.
